Baseline Drift Estimation for Air Quality Data Using Quantile Trend Filtering

### 2019-04-04 Manuscript/detrendify_aoas.tex
Manuscript edits and updated figures, draft ready for comments
update plots for full day
added another sentance to application section

\subsection{Long series of air quality measurements}
\label{sec:long-app}
\Alg{admm} was used to removed the baseline drift from the full day of data  (\Fig{raw_spod}) consisting of 86,401 observations per SPod and compared to the series detrended using the \texttt{qsreg} trends estimated using non-overlapping 2 hour windows. As in the shorter illustration, the \texttt{detrendr} method results in generally higher VI scores than the \texttt{qsreg} method (\Fig{vi_day}). The \texttt{detrendr} method also results in better correlation in the detrended series as is illustrated in (\Fig{scatter_day}).

>>>>

\subsection{Long series of air quality measurements}
\label{sec:long-app}
\Alg{admm} was used to removed the baseline drift from the full day of data  (\Fig{raw_spod}) consisting of 86,401 observations per SPod and compared to the series detrended using the \texttt{qsreg} trends estimated using non-overlapping 2 hour windows. As in the shorter illustration, the \texttt{detrendr} method results in generally higher VI scores than the \texttt{qsreg} method (\Fig{vi_day}). The \texttt{detrendr} method also results in better correlation in the detrended series as is illustrated in (\Fig{scatter_day}). The Spearman correlation coefficients for SPods a and b, SPods a and c, and SPods b and c after removing the 5\textsuperscript{th} quantile trend using \texttt{detrendr} were 0.37, 0.75, and 0.43, compared with 0.07, 0.24, and 0.16 using \texttt{qsreg}. The noise variance was higher for SPod b than for SPods a and c resulting in lower correlation and higher VI values for the ab and bc metrics compared with ac.
